---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
p {
  font-size: 15px; 
  font-family: Georgia, serif;
}
body {
  background-color: #ffe6f0;
}
h2 {
  color: #cc3366;
  font-family: Georgia, serif;
}
h3 {
  color: #cc3366;
  font-family: Georgia, serif;
}
```

## Trends in Auckland City Bus Commutes: Delays, Passenger Counts & Experience Ratings!

```{r}
library(tidyverse)

logged_data = read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTBY2IbpkoUxwuQU9PQPZ8ZFhijSt9TGZR_C_GrinzW3ktfSkQ62BKl4wrakwISwegdRjwZ7TsmvXMx/pub?gid=2092472461&single=true&output=csv")

# rename columns 2:5, keeping column 1 the same
latest_data <- logged_data %>%
  rename(bus_arrival = 2,
         bus_arrival_difference = 3,
         number_of_passengers = 4,
         experience = 5)

# summary of values
min_experience = min(latest_data$experience)
max_experience = max(latest_data$experience)
# get frequency of experiences equal to min or max
min_frequency = sum(latest_data$experience == min_experience)
max_frequency = sum(latest_data$experience == max_experience)
# max valuing using min() function as negative numbers mean the bus is late 
max_wait_time = min(latest_data$bus_arrival_difference)
# the earliest a bus arrived by minutes
max_early_time = max(latest_data$bus_arrival_difference)

```

The maximum wait time for a bus was `r max_wait_time` minutes (the negative sign shows it was delayed), while the earliest a bus arrived was `r max_early_time` minutes.

The minimum experience rating recorded was `r min_experience` stars with a frequency of `r min_frequency` and the maximum recorded was `r max_experience` stars with a frequency of `r max_frequency`.

### Bar Charts

```{r}

# bar graph of frequency of experience ratings

experience_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = experience),
           fill = "#C3B1E1") +
  labs(title = "Experience of Bus Rides",
       subtitle = "1 = Poor, 5 = Amazing",
       caption = "Source: Google Forms",
       x = "Experience Rating",
       y = "Frequency")

paste("This Bar chart here shows the frequency of different experience ratings of a bus ride")

experience_plot

# bar graph of frequency of number of passengers

passenger_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = number_of_passengers),
           fill = "#FFB7C5") +
  labs(title = "Frequency of Bus Passengers",
       caption = "Source: Google Forms",
       x = "Number of Passengers in The Bus",
       y = "Frequency")

paste("Meanwhile this Bar chart here shows the frequency of number of passengers in the bus at the time of submission")

passenger_plot

```




